\input{prereg.tex}
\begin{document}
No weahter is more gentle and absurd than the drunk southern winds in France
when you are surrounded by people of immense wealth and fame and the rain is
soft and the people beautiful. The chatter was sprinkled throughout the domain
amongst the torches, the rings of lips announcing mergers and occasions for
more orgies, more orgies and more life.  Here parties were not a vulgar tornado
one might see on a loft in Manhattan those parties were maelstroms where the
currents and eddies were largely swirling beneath the surface or around the
edges of things.\\

The idea of a place I've never been to\\

The old supermodel was named Anna  and had perfectly wrinkled skin; she had
always refused to undertake plastic surgery unless completely necesserary. She
had long blond hair parted in the middle, waving down her shoulders. Her shoes
were of a tame gold as a call back to her fair freckled skin. The walls were
stark and grey, with old paint that had been through two wars.\\

She was standing on one foot the other resting on the arm of the chair facing
her and she was contemplating the lean muscles emenating from her. She seemed
amused at a situation, not the present one but a distant blur from days of fame
and exhuberance.\\



Not that she wasn’t famous anymore, but she had lost control on her image in
the eyes of the camera. The photographer was softly handsome and young. He war
wearing a white wife beater and beige chinos. He was making those motions of
the camera one expects a fashion photographer to make, leaning and tilting and
passing rapid comments.  The house was both aristocratic and falling in demise.
The mouldings were preserved and were reminiscent of another age of decadence.
The room was long and rougly narrow, lit by large candles on the walls. They
were light bulbes too, disperesed and hanging from rusty wires which seemed
like a fire hazard but the photographer didn’t care as it contributed to the
atmosphere and the rustiness which is something he was chasing through his
work, rusty buildings rusty personnalities, oxydised faces searching for their
glasses. The old super model was walking slowly on the persian carpet in a way
reminescent of  her professionnel days, stopping here and there to look in an
abyss she created with piercing and detached eyes, slightly asiatic eyes with
colors that made you guess each time you met het and proceed to stare to
finally mae your mind. I did not care that much for the scene except for the
old supermodel who always put me in a trance when she seemed to be travelling
to her own twenties, drunk on champagne and candelabres and velvet curtains
which were slowly moving to the rythm of a breeze.\\ \clearpage

The room didn’t seem to have a purpose other than drinking champagne and
practicing cat walks for a photographer. At the end of the carpet the old
supermodel bent down, mostly using her back and not her knees and is usually
recommended, arching her buttocks to the candlelight and picked up a ginger cat
while parting her lips in a very unhappy sensuous smile.  Despite the numerous
light sources the room was dark which made the room look even more
aristocratic, smelling of old money before light fixtures were mass produced
and you could analyze the not so smooth skin of the teenager making you pay for
your medication at the pharmacy when you had a small breakdown and needed just
a couple of xanax. The old supermodel picked up the cat and kept on walking
towards the end of the room where the bar was. It was made of solid rock and
had bottles of champagne, bourbon and scotch and no mixers because the liquor
was good enough and mixing demanded a butler who was not there but driving back
the son of some admiral of the British army who had drank too much champagne
and was looking for a less anachronistic decadence with techno music and
beautiful trans people in dark rooms. The house was close to the sea, one only
needed to walk for some minutes on cobbled stairs and arched passage ways to
get to an old dock of polished stones where small boats could unload more
champagne and bourbon and liquors. The old supermodel had gotten here by car,
an aston martin of the 60’s, of a dark green which had commended the admiration
of the admirals son who was very much into old cars, not for speeding down
alleys but for cruising the costa del sol and the costa del brava and the cote
d’azures and any sunny coast which had a latinate name. The bar was much bigger
room than the one used for the improptu photo shoot as the party was more
important than the art. The party was the whole reason for the art in the first
place. The young photographer had always enjoyed greek mythology and and wanted
to be a classissists when he was even younger but he soon realized that it was
better to climb to olympus than read old poets telling its tales and after
obtaining his degree from a very prestigious liberal arts college he had
decided to find where the party was, even though there wasn’t really a party.
Even though he intriscally knew that the conversations were not more
interesting or fulfilling at the party one still needed to be at the party. For
if you didn’t get to be at the party you were somewhere whose whole raison
d’être was to feed the gushing streams that would scale the mountains and reach
it and rinse the mouths of singers with whistle registers and breasts like the
sweetest raspberries known to primitive rousseans savages. The bar was in a
large room with more carpetting and french royal furniture with big armrests
which could be dated to some Louis king but nobody dared give a roman number to
them as it would have seemed out of touch with the atmosphere. The windows
behind the purple curtains were large with large windowpanes and white paint on
the old wood. The large room was in the shape of a large circle with no center
because the point was that the bar was the center irrespective of the geometry.
Two men were sitting on two sofas discussing their poetry and a voluptuous
woman with curly red hair was extravantly sitting on the edge of one of the
sofas peering dreamly at the windowpanes as melancholy was important. The
laughter emanating was noth wide and britle. When the old model got to the bar
she asked if anybody “fancied some more champagne” to which the coronel’s son
who didn’t like to be confused to the admiral’s son due to some ancestral
animosity between them  “reckoned it was a grand idea” and “wasn’t it a grand
night, the rain being just soft and moody enough”. A jazz band played in the
corner adjacent to the two sofas and the red haired woman playing cole porter’s
song very softly with a trumpet a double bass and a piano and no drums becaused
the rain on the shingles provided the whispery rythm that was needed. There had
been swing songs and dancing earlier but it seemed out of touch at this point
and it seemed obvious that dancing was out of the question at this hour. The
photographer laid down his camera on the bar without removing the lense as it
would be needed later after more champagne had been poured. He observed a
distant smile from himself in the mirror behind the bar and noticed the model’s
dress was undulating to the rythm of a metaphorical wind. It was a black dress
with a deep décolleté and an open leg from a soft fabric which made a rustling
sound as it discovered the tan creeses of her skin. She was still holding the
cat in her right arm as the colonel’s son was pouring champagne in her flute
and they drank the first sip together to a charming evening and she walked
towards the exit where the path to the water started. The colonel’s son was
named eric and was gracious in his conversation with the photographer who was
an intruder in the party, as a participant at least instead of a background
character, by all standards. 

It was only two months before the party that the photographer had made the
decision to leave NYC for France after his last gig for Vogue magazine. The
editor of the internet outlet for the company had been madly in love with him,
for his soft voice and effeminate posture which revealed a masculinity which
was long gone in the industry where a very macho form of feminity had
established itself as the personalita franca. He wasn’t a genius in any sense
of the profession, everybody agreed on that. He hadn’t developped what could be
called a vision and although he off course knew the ins and outs and various
proceedings he hadn’t elevated himself. What he had was an uncanny
psychological instinct into the workings of the mind of an anxious model, a
capricious art director and a quite simply crazy sponsor. He approached all
parties involved with a candor which seemed to put all parties involved at ease
at an instant, both elevating and grounding the process of developping a new
campaign. Everybody refered to him as Jimmy eventhough his real name was
probably a good old strong anglo-Norman regal syllable composition such as
Richard or Henry. Jimmy did not show his surprise when the colonel’s son
mentioned he had a boat, for he expected it to be the privilege of the
admiral’s son to own one. Navy and traditions and what not. It was very naive
of him and he knew it. Off course both of them owned boats, one was expected to
go sailing to corsica in the spring. It was just the right and obvious thing to
do.  I followed their conversations from my chair next to the curvy women with
curly red hair, in a drunken absent stare probably. I was not used to this
level of decadence, now I could moderate myself in front of an open bar of
cheap liquor and house wine but what was served here was 50’s years old
champagne and obscure islay scotches from private reserves. I could not abstain
myself from these pleasures in an orderly fashion. The woman with red hair was
holding my right hand to her cheek and was doing what we might call in a haste
palm reading but she seemed to be pulling my life from thin air unpreoccupied
by the skin creeks, it was performed as in a sensual ritual designed to magnify
the cognitive experience.  She was singer and had great success at it. She had
started within the confines of the pop song industry restraining her prestige
for the money but had slowly matured and blossomed into a multi faceted
technical prodigy with a great taste for new song writers and colorful
adaptations, sometimes showing virtuosity in jazz scating on complex
progressions or simply perfectly capturing a nirvana song into a an actualized
impressionistic take on contemporary society. Or at least that’s how I think I
answered her when she asked me what I thought of her singing. She had very nice
breasts and life affirming cheekbones. She was not interested in the end, she
considered me as an old child. Not by age, she just told I will ever be a man
child, no matter how much wisdom I would accumulated eventually. It was the
kind of rejection that made sense in this environment, a “sorry, I have a
boyfriend” or a thing of the sort would have seemed gauche or rather brutish. A
coherent set of aesthetic attitudes had to be taken into account. It was what
distinguished aritstocracy from merely rich. 

That was before I was too drunk to elaborate on nothing as was my only means of
conversation at that point in my life. She 

\clearpage \section{midway}


\hfill \textit{\small{-Remember that time Toby asked the prince of Luxembourg
for a double old-fashioned}}\\

\hfill \small{-You see the thing about modern theater, is that absurdity has
become normalized}\\

\textit{\small{-YES, like he was some waiter, and then when the prince said
what in a condescending tone (chuckles) when he said 'what did you just
say'}}\\

\hfill\small{-Toby just repeated louder: I SAID A GIN TONIC PLEASE SIR}\\ -So
tell me Jimmy what made you leave the bustling of NYC for this antequated place
-I guess that I am trying to “fuir l’ennuie” -What is that French? You know
son, it is not because you’re in France that you have to speak French, quite
the opposite I reckon actually. But it rhymes, so I guess that’s the principal.
I’ve found that saying something does not matter as much as long as it sounds
nice -Yes rhyming is most important aspect, I don’t think I’ve said anything
interesting that didn’t rhyme since I was fifteen -Do you consider yourself an
interesting person then -I guess it depends on the context -Well I for one
consider you a very interesting chap old sport, I’m glad you could come here
and inject some young blood in this little community. You know those circles
tend to ossify. It was Marie that took you along wasn’t it.  -Yes I was working
at this gallery in Cannes, she was there on the latest opening night, she was
the model for most of the pictures. It was actually an installation-performance
you could call it. She was there as herself next to her representations,
something about the image presented to the eye through the lens as opposed to
the full bodied presence -This gallery, it is the fontaine-pied right? Yes I
have been there a couple time, we have a yacht, 52 footer docked at the marina
and my wife and I—seperated mind you—we used to go there after a stroll, have a
drink with Monsieur Rougeau. Was this a connection from NYC?  -Well to tell you
the truth my van broke down in front of the place, I was planning on going to
Italy but then Réjean offered me his help. I took him for a local mechanic at
the time, very nice man. After I mentioned my work and you know so on and so
forth how conversation goes he told me their latest assistant had gone on a
sort of spiritual journey if I understood him correctly, no sign of coming back
and they needed a hand from somebody that “had a keen eye for aesthetic
necessities” was how he put it. I am going back next week, this is a company
vacation. In america they would call it team building but French people seem to
just call it life down here -Oh well don’t generalize here, you’ve fell by
chance on the most idiosyncratic elements of the French aristocracy, I know
some people in Paris, they would have sneered at you until you can produce
evidence of notable social connections. 


\end{document}
